---
title: "p8105_hw6_hw2861"
author: "Hongmiao Wang"
date: "2022-12-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 2
The Washington Post has gathered data on homicides in 50 large U.S. cities.

### create Create a city_state variable and a binary variable indicating whether the homicide is solved. 
```{r homicides}
homicide_df = 
  read_csv("./Data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    victim_age = as.numeric(victim_age),
    status = case_when(
      disposition == "Closed without arrest" | disposition == "Open/No arrest"   ~ 0,
      TRUE ~ 1)) %>% 
    filter(!city_state %in% c("Tulsa,AL", "Dallas,TX", "Phoenix,AZ", "Kansas City,MO"))%>% 
    filter(victim_race == "White"| victim_race == "Black")
```
The binary variable indicating whether the homicide is solved is called " status". Some cities have been omitted.


### For the city of Baltimore, MD, use the glm function to fit a logistic regression.

* Resolved vs unresolved as the outcome and victim age, sex and race as predictors.
```{r}
balt_glm = 
  homicide_df %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(status ~ victim_age + victim_race + victim_sex, data = ., family = binomial())  


  broom::tidy(balt_glm) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  select(term, OR, CI_lower,CI_upper) %>% 
  filter(term == "victim_sexMale") %>% 
  knitr::kable(digits = 3)
```


### Now run glm for each of the cities in my dataset

* Extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims.
```{r}
city_glm = 
  homicide_df %>% 
  group_by(city_state)%>% 
  nest() %>% 
  mutate(
    models= map(data, ~glm(status ~ victim_age + victim_race + victim_sex, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  select(term, OR, CI_lower,CI_upper) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, term, OR, CI_lower,CI_upper) %>% 
  knitr::kable(digits = 3)
```

I created a dataframe with estimated ORs and CIs for each city.

